\mynewpage
\chapter{To Do}\draftnote{Warning: may be obsolete}
\paragraph{Papadopoulo's $L1$ Equation for Occluding Contours}
\begin{enumerate}
\item Forget occluding contours for now. Understand why $\beta_t$ brings in curvature $\kappa$. Understand
Papadopoulo's Lie derivatives.
\item Understand how to represent $(\gama\times\t)_t$ in terms of surface
curvature.
\item Try to get curvature formula for normal parametrization. Go through usual
proof first.
\item Study more Differential Geometry
\item Type about the redundant third-order L2, L3 equations in the review of
papadopoulo, summarizing the email I got.
\item Study Papadopoulos's experiments and numerics. Try to reproduce them.
\item Explore examples and conduct synthetic experiments in order to test the correctness of the
formulas.
\item Integrate proofs of flow and depth formulas (see notes 4/15/18 for
details).
\item Write depth formula for any direction. Interpret the result.
\end{enumerate}

\paragraph{Others}
\begin{itemize}
\item Notation and other material are now valid only in PAMI-theory.
\end{itemize}

\paragraph{Edge classification and Occluding contours}
\begin{enumerate}
\item GOAL (jul'07): close loose ends, have notes, literature review, and math
study finished by August'07.
\item Type occluding contour summaries.
\begin{itemize}
  \item Review geodesic torsion and interpretation.
\end{itemize}
\item Finish corrections on scattered mark-ups from Ben
\begin{itemize}
\item double-check table of symbols and improve.
\end{itemize}
\item Include the figures about the numerical experiments with pov-ray
\item Finish interpreting occluding contour equations, especially the role of
conjugacy. Intepret depth formula, and $\gama_t$.
\item Occluding contours: settle the formulas for image velocities for the case of
planar perspective projection (not spherical perspective).
\item Study more diff geometry
  \begin{itemize}
  \item O'Neill notation - first chapters only
  \item Excercises from Carmo to fix concepts
  \end{itemize}
\item Read our paper summaries
\item Read remaining Koenderink papers
\item Play more with the optimization of our differential shading equations
\item Integrability constraint: can it help our equations? Why decouple
geometric normals and photometric normals (``V'' vector field)?
\item Why multiple light sources give immunity to bas-relief? why the more
light sources, the better accuracy? (Cipolla and
Vogiatzis CVPR paper)
\item Bas-relief ambiguity for the perspective case?
\item Summarize remaining occluding contour papers based on frontiers
\item Carry on research relating slant and $\frac{\|\nabla\|}{\depth}$.
\item Finish figures, esp. Donati and Stolfi
\item Summarize remaining important literature
\item Study kinematics in ``Physics for Scientists and Engineers'' in order to
interpret the infinitesimal rotation as a screw vector and build intuition.
\end{enumerate}
